A Convolutional Neural Network for Outsole Recognition\tnoteref{t1}

### 2019-06-20 paper/paper.Rnw
missed a reference!

The horizontal band in \autoref{fig:confusion_matrix} indicates that quadrilaterals are predicted more often than they should be for every true label. Similarly, polygons, stars, and triangles produce a \svp{moderate} number of false positive predictions \svp{in} other categories, as evidenced by the vertical bands for these categories. \fix{I don't really see it for stars...} It is also apparent that circles and text are commonly confused, which supports our earlier obsesrvartions from \autoref{fig:circle-text-consistency} that these two classes are difficult for the model to distinguish, \svp{in part because circles are relatively common components of latin script characters.}

>>>>

The horizontal band in \autoref{fig:confusion-matrix} indicates that quadrilaterals are predicted more often than they should be for every true label. Similarly, polygons, stars, and triangles produce a \svp{moderate} number of false positive predictions \svp{in} other categories, as evidenced by the vertical bands for these categories. \fix{I don't really see it for stars...} It is also apparent that circles and text are commonly confused, which supports our earlier obsesrvartions from \autoref{fig:circle-text-consistency} that these two classes are difficult for the model to distinguish, \svp{in part because circles are relatively common components of latin script characters.}
